\hyt{ahorsewithnoname}
\song{A Horse With No Name}

\nv\textit{\normalsize{Správné ladění pro tuto píseň je D-E-d-g-h-d. Celou dobu se pak opakují akordy Em\7 (2-0-2-0-0-0) a D\6 (0-2-0-2-0-0-0), přičemž v refrainu je akord Em\7 nahrazen akordem Em\9 (2-0-2-0-0-2).}}

\vers{1}{
On the \chord{Em\7}first part of the \chord{D\6}journey I was \chord{Em\7}lookin' at all the \chord{D\6}life.\\
There were \chord{Em\7}plants and birds and \chord{D\6}rocks and things, there were \chord{Em\7}sand and hills and \chord{D\6}rings.\footnote{Kruhové skvrny bez vegetace, ohraničené trávou zvýšeného vzrůstu. Objevují se v savanách Namibské pouště v jihozápadní Africe, ale také v regionu Pilbara na severozápadě Austrálie. Studie ukazují, že tyto kruhy procházejí životním cyklem trvajícím 30 až 60 let a~dosahují průměru až 12 m. Jejich původ byl dlouho záhadou. Jako příčina jejich vzniku byla v roce 2012 označena \uv{zemědělská} aktivita termitů. Tato teorie byla ovšem označena jako nepravdivá z důvodu záměny korelace a kauzality. (Termiti kruhy využívají, ale netvoří.) O~rok později byla představena teorie, která  tvrdí, že tyto kruhy jsou důsledkem soutěže mezi různými druhy trav. Jsou udržovány, protože se v nich koncentrují živiny pro vyšší druhy trav, které pak rostou na jejich obvodu.}\\
The \chord{Em\7}first thing I met was a \chord{D\6}fly with a buzz and the \chord{Em\7}sky with no \chord{D\6}clouds.\\
The \chord{Em\7}heat was hot and the \chord{D\6}ground was dry, but the \chord{Em\7}air was full of \chord{D\6}sound.
}

\refrain{
I've \chord{Em\9}been through the desert on a \chord{D\6}horse with no name,\\
it felt \chord{Em\9}good to be out of the \chord{D\6}rain.\\
In the \chord{Em\9}desert you can re\chord{D\6}member your name,\\
'cause there \chord{Em\9}ain't no one for to \chord{D\6}give you no pain.\\
\rep{La, \chord{Em\9}la la la \chord{D\6}lala la lala \chord{Em\9}la la \chord{D\6}la.}
}

\vers{2}{
After two days in the desert sun  my skin began to turn red.\\
After three days in the desert fun I was looking at a river bed.\\
And the story it told of a river that flowed made me sad to think it was dead.\\
You see,
} \refsm{}

\vers{3}{
After nine days I let the horse run free, 'cause the desert had turned to sea.\\
There were plants and birds and rocks and things, there was sand and hills and rings.\\
The ocean is a desert with its life undergroud and perfect disguise above.\\
Under the cities lies a heart made of ground, but the humans will give no love.\\
You see,
} \refsm{}

\cod{
\rep{La, la la la lala la lala la la la.} \textit{fade out}
}
\newpage
