\hyt{alwayslookonthebrightsideoflife}
\song{Always Look on the Bright Side of Life}

\vers{1}{
Some \chord{Am}things in life are \chord{A\dm}bad, they can \chord{G}really make you \chord{G\6}mad,\\
\chord{Am}other things just \chord{A\dm}make you swear and \chord{G}curse.\chord{G\6}\\
When you're \chord{Am}chewing on life's \chord{A\dm}gristle, don't \chord{G}grumble, give a \chord{E\7}whistle,\\
and \chord{A\7}this'll help things turn out for the \chord{D\7}best.
}

\refrainn{1}{
And \chord{G}always \chord{Em\7}look on the \chord{Am}bright \chord{D\7}side of \chord{G}life.\chord{Em\7}\nc\chord{Am}\nc\chord{D\7}\\
\chord{G}Always \chord{Em\7}look on the \chord{Am}light \chord{D\7}side of \chord{G}life.\chord{Em\7}\nc\chord{Am}\nc\chord{D\7}
}

\vers{2}{
If life seems jolly rotten, there's something you've forgotten,\\
and that's to laugh and smile and dance and sing.\\
When you're feeling in the dumps, don't be silly chumps,\\
just purse your lips and whistle -- that's the thing.
} \refsm{1}

\vers{3}{
For life is quite absurd and death's the final word,\\
you must always face the curtain with a bow.\\
Forget about your sin -- give the audience a grin,\\
enjoy it -- it's your last chance anyhow.
}

\refrainn{2}{
So always look an the bright side of death,\\
just before you draw your terminal breath.
}

\vers{4}{
Life's a piece of shit, when you look at it,\\
life's a laugh and death's a joke, it's true.\\
You'll see it's all a show, keep 'em laughing as you go,\\
just remember that the last laugh is on you.
} \refsm{1} \note{fade out}
