\hyt{greensleeves}
\song{Greensleeves}
\hyl{dobrodruzstvisbohempanem}{Dobrodružství s bohem Panem}
\hyl{romance16leta}{Romance 16. léta}

\vspace{3mm}
\note{capo 3}

\vers{1}{
\chord{Am}Alas, my \chord{C}love, you \chord{G}do me \chord{Em}wrong, to \chord{Am}cast me off dis\chord{E}couteously.\\
For \chord{Am}I have \chord{C}loved you \chord{G}well and \chord{Em}long, de\chord{Am}lightning \chord{E\7}in your \chord{Am}company.
}

\refrain{
\chord{C}Greensleeves was \chord{G}all my \chord{Em}joy, \chord{Am}greensleeves was \chord{E}my delight.\\
\chord{C}Greensleeves was my \chord{G}heart of \chord{Em}gold and \chord{Am}who, but my \chord{E\7}lady \chord{Am}greensleeves.
}

\vers{2}{
Your vows you've broken, like my heart, oh, why did you so enrapture me?\\
Now I remain in a world apart, but my heart remains in captivity
} \refsm{}

\vers{3}{
I have been ready at your hand, to grant whatever you would crave.\\
I have both wagered life and land, your love and good-will for to have.
} \refsm{}

\vers{4}{
If you intend thus to disdain, if does the more enrapture me.\\
And even so, I still remain a lover in captivity.
} \refsm{}

\vers{5}{
My men were clothed all in green and they did ever wait for thee;\\
all this was gallant to be seen and yet thou wouldsts not love me.
} \refsm{}

\vers{6}{
Thou couldst desire no earthly thing, but still thou hadst it readily.\\
Thy music still to play and sing;
and yet thou wouldst not love me.
} \refsm{}

\vers{7}{
Well, I will pray to God on high, that thou may constancy mayst see\\
and that yet once before I die, thou wilt vouchsafe to love me.
} \refsm{}

\vers{8}{
Ah, greensleeves, now farewell, adieu, to God I pray to prosper thee.\\
For I am still thy lover, true, come once again and love me.
} \refsm{}
\newpage
