\hyt{nancymulligan}
\song{Nancy Mulligan}

\vers{1}{
\chord{Am}I was twenty-four years \chord{F}old, when I \chord{G}met the woman I would \chord{Am}call my own,\\
twenty-\chord{Am}two grand kids now \chord{F}growing \chord{C}old in that \chord{F}house, that your \chord{G}brother \chord{Am}bought ya.
}

\vers{2}{
On the summer day when I proposed, I made that wedding ring from dentist gold\\
and I asked her father, but her daddy said no, you can't marry my daughter.
}

\refrain{
\chord{C}She and I went \chord{F}on the \chord{C}run, \chord{G}don't care about r\chord{F}eli\chord{C}gion,\\
\chord{C}I'm gonna marry the \chord{F}woman I \chord{C}love, \chord{F}down by the \chord{G}Wexford \chord{Am}border.\\
She was Nancy Mulligan, and I was William Sheeran,\\
she took my name and then we were one, down by the Wexford border.
}

\vers{3}{
Well I met her at Guy's in the second world war and she was working on a soldier's ward,\\
never had I seen such beauty before the moment, that I saw her.}

\vers{4}{
Nancy was my yellow rose and we got married wearing borrowed clothes,\\
we got eight children now growing old, five sons and three daughters.
} \refsm{}

\solo{\rep{\chord{C}Di da-da-da-da-da di-da-\chord{F}di, \chord{G}di da-da-da-da-da di-da-di, da da\\
\chord{C}di da-da-da-da-da di-da\chord{F}di, \chord{G}di da-da-da-da-da \chord{C}di.}
}

\vers{5}{
From her snow white streak in her jet black hair, over sixty years I've been loving her,\\
now we're sat by fire in our old armchairs, you know, Nancy, I adore ya.
}

\vers{6}{
From a farm boy born near Belfast town, I never worried about the king and crown,\\
'cause I found my heart upon the southern ground, there's no difference I assure ya.
} \refsm{}
\newpage
