\hyt{pianoman}
\song{Piano man} \interpret{billyjoel}{Billy Joel}

\ns
\intro{Dm\7 D\dm, akordy jako ve sloce} \solon{1}{C F G F $\times$ 2}\vspace{-30pt}

\vers{1}{
It's \chord{C}nine \chord{G/H}o'clock on a \chord{F/A}Saturday,\chord{C/G}\nc the \chord{F}regular \chord{C/E}crowd shuffles \chord{D\7}in. \chord{G}\\
There's an \chord{C}old man \chord{G/H}sittin' \chord{F/A}next to me,\chord{C/G}\nc makin' \chord{F}love to his \chord{G}tonic and \chord{C}gin.
}

\vers{2}{
He says, "Son, can you play me a memory? I'm not really sure how it goes,\\
but it's sad and it's sweet and I knew it complete\\
when I wore a younger man's clothes."
}

\solon{2}{
\chord{Am}La, la-\chord{Am/G}la, di-di-\chord{D/F\kk}da,\nc\chord{D}\nc\chord{Am}\mm la-\chord{Am/G}la, di-di-\chord{D/F\kk}da,\nc \chord{D}\mm da-\chord{G}dum.\chord{G/F}\nc\chord{C/E}\nc\chord{G\7/D}
}

\refrain{
Sing us a song, you're the piano man, sing us a song tonight.\\
Well, we're all in the mood for a melody, and you've got us feelin' alright.
} \textbf{S1.}

\vers{3}{
Now John at the bar is a friend of mine, he gets me my drinks for free,\\
and he's quick with a joke or to light up your smoke,\\
but there's some place that he'd rather be.
}

\vers{4}{
He says, "Bill, I believe this is killing me," as the smile ran away from his face,\\
"Well, I'm sure that I could be a movie star if I could get out of this place".
} \textbf{S2.}

\vers{5}{
Now Paul is a real estate novelist, who never had time for a wife.\\
And he's talkin' with Davy, who's still in the Navy and probably will be for life.
}

\vers{6}{
And the waitress is practicing politics, as the businessmen slowly get stoned.\\
Yes, they're sharing a drink they call loneliness,\\
but it's better than drinkin' alone.
} \refsm{} \textbf{S1.}

\vers{7}{
It's a pretty good crowd for a Saturday, and the manager gives me a smile,\\
'cause he knows that it's me they've been comin' to see,\\
to forget about life for a while.
}

\vers{8}{
And the piano, it sounds like a carnival, and the microphone smells like a beer,\\
and they sit at the bar and put bread in my jar\\
and say, "Man, what are you doin' here?"
} \textbf{S2.} \refsm{} \textbf{S1.}
\newpage