\hyt{rockyraccoon}
\song{Rocky Raccoon} \interpret{beatles}{The Beatles}

\intro{
Now \chord{Am\7}somewhere in the Black Mountain Hills of Dakota,\\
there lived a \chord{D\7\4}young boy name of Rocky Racc\chord{D\7}oon\\
and \chord{G\7}one day his woman ran of with a\chord{C}nother guy,\\
\chord{C\bas{H}}hit young Rocky in the \chord{Am\7}eye. Rocky didn't like that, he said \enquote*{I'm \chord{D\7}going to get that boy.}\\
So one \chord{G\7}day he walked into town and booked himself a room in the \chord{C}local saloon.
}

\vers{1}{
\chord{Am\7}Rocky Raccoon checked \chord{D\7}into his room \chord{G\7}only to find Gideon's \chord{C}Bible.\footnote{Je typické, že v hotelových nočních stolcích bývají Gedeonské Bible, takzvané gedeonky, vydávané Mezinárodním svazem Gedeonů. Tento svaz je mezidenominační společenství křesťanů (zvláště podnikatelů a odborných pracovníků), kteří jsou členy protestantských/evangelikálních církví. Inspirováni podobenstvím o Rozsévači, Gedeoni bezplatně distribuují Bibli na různá místa, jako hotely, školy, nemocnice, vězení, státní instituce\dots Tyto Bible nejsou určeny pro církve, ale pro nevěřící. Gedeoni také drží nepřetržitý modlitební řetěz za všechny země světa (např. za Česku republiku se modlí každý 9. den v měsíci).}\chord{C\bas{H}}\\
\chord{Am\7}Rocky had come eq\chord{D\7}uipped with a gun to \chord{G\7}shoot off the legs of his \chord{C}rival.\chord{C\bas{H}}\\
His \chord{Am\7}rival, it seems, had \chord{D\7}broken his dreams by \chord{G\7}stealing the girl of his \chord{C}fancy.\chord{C\bas{H}}\\
Her \chord{Am\7}name was Magill, and she \chord{D\7}called herself \enquote{Lil}, but \chord{G\7}everyone knew her as \chord{C}Nancy.\chord{C\bas{H}}
}

\vers{2}{
Now, she and the man, who called himself Dan were in the next room in the hoedown.\\
Rocky burst in, and grinning a grin, he said, \enquote*{Danny, boy, this is a showdown.}\\
Bud Daniel was hot, he drew first and shot and Rocky collapsed in the corner.
}

\refrain{
\chord{Am\7}Da-n-da da da-n-da da da\dots \chord{D\7}\nc\chord{G\7}\nc\chord{C}\nc\chord{C\bas{H}}
}

\vers{3}{
Now, the doctor came in, stinking of gin and proceeded to lie on the table.\\
He said, \enquote*{Rocky, you met your match.}, but Rocky said \enquote*{Doc, it's only a scratch\\
and I'll be better\dots I'll be better, doc, as soon as I am able.}
}

\vers{4}{
Now, Rocky Raccoon, he fell back in his room only to find Gideon's Bible.\\
Gideon checked out, and he left it no doubt to help with good Rocky's revival.
} \refsm{}
\newpage
