\hyt{thesoundofsilence}
\song{The Sound Of Silence} \interpret{simongarfunkel}{Simon \& Garfunkel}

\vers{1}{
\chord{Am}Hello darkness, my old \chord{G}friend, I've come to talk with you a\chord{Am}gain,\\
becaouse a \chord{C}vision softly\chord{F} cree\chord{C}ping, left its seeds while I was\chord{F} slee\chord{C}ping.\\
And the \chord{F}vision, that was planted in my \chord{C}brain still re\chord{Am}mains\\
\chord{C}within the \chord{G}sound of \chord{Am}silence.
}

\vers{2}{
In restless dreams I walked alone narrow streets of cobble-stone.\\
'Neath the halo of a streetlamp, I turned my collar to the cold and damp,\\
when my eyes were stabbed by the flash of a neon light, that split the night\\
and touched the sound of silence.
}

\vers{3}{
And in the naked light I saw ten thousand people, maybe more.\\
People talking without speaking, people hearing without listening,\\
people writing songs, that voices never share and no one dare\\
disturb the sound of silence.
}

\vers{4}{
\enquote{Fools!,} said I, \enquote{You do not know, silence like a cancer grows.}\\
\enquote{Hear my words, that I might teach you, take my arms, that I might reach you!}\\
But my words like silent raindrops fell,\\
and echoed in the wells of silence.
}

\vers{5}{
And the people bowed and prayed to the neon god, they made.\\
And the sign flashed out its warning in the words, that it was forming.\\
And the signs said \enquote{The words of the prophets are written on the subway walls and tenement halls.}\\
And whisper'd in the sound of silence.
}
\newpage
