\hyt{twistandshout}
\song{Twist And Shout} \interpret{beatles}{Beatles}
\hyl{labamba}{La Bamba}

\vers{1}{
Well shake it up \chord{D}baby now, \textit{(}\chord{G}\textit{shake it up} \chord{A}\textit{baby)}\\
\chord{A\7}twist and \chord{D}shout! \textit{(}\chord{G}\textit{twist and} \chord{A}\textit{shout)}\\
Come on, come on, \chord{A\7}come on, come on, \chord{D}baby now, \textit{(}\chord{G}\textit{come on} \chord{A}\textit{baby)}\\
come on and work it on \chord{D}out. \textit{(}\chord{G}\textit{work it on} \chord{A}\textit{out, ooh)}
}

\vers{2}{
Well work it on out, \textit{(work it on out)},\\
you know, you look so good! \textit{(look so good)}\\
You know you got me goin' now, \textit{(got me goin')}\\
just like I knew you would. \textit{(like I knew you would, ooh)}
}

\vers{3}{
	= \mm\textbf{1.}
}

\vers{4}{
You know you twist it little girl, \textit{(twist it little girl)}\\
you know, you twist so fine. \textit{(twist so fine)}\\
Come on and twist a little closer now, \textit{(twist a little closer)}\\
and let me know that you're mine. \textit{(let me know you're mine, ooh)}
}

\bridge{
\chord{A}Ahh, ahh, ahh, \chord{A\7}ahh, ahh, wow, yeah!
}

\vers{5}{
Baby now, \textit{(shake it up, baby)}\\
twist and shout! \textit{(twist and shout)}\\
Come on, come on, come on, come on, baby now, \textit{(come on baby)}\\
come on and work it on out. \textit{(work it on out, ooh)}
}

\vers{6}{
	= \mm\textbf{4.}
}

\vers{7}{
Well shake it, shake it, shake it baby now. \textit{(shake it up, baby)}\\
Well shake it, shake it, shake it baby now. \textit{(shake it up, baby)}\\
Well shake it, shake it, shake it baby now. \textit{(shake it up, baby)}\\
\chord{A}Aah, aah, \chord{A\7}aah, aah. \chord{A}\nc\chord{B}\nc\chord{H}\nc\chord{C}\nc\chord{C\kk}\nc\chord{D}\nc\chord{D\9}
}

\newpage
